\section{System Overview}
\label{sec:system}
\textsc{Synopsis} is implemented on top of the Neptune stream processing system \cite{buddhika2016neptune} as a specialized layer for geospatial data.
In this section, we will briefly introduce Neptune followed by a discussion on the design of \textsc{Synopsis}.

\subsection{Neptune}
Neptune is a distributed stream processing system that is designed to cope with application requirements such as high volumes of small stream packets, high and variable data rates, and heterogeneity within stream processing jobs.
Satisfying these requirements imposes various system level challenges including possible buffer overflow errors, increased number of context switches, object creation overhead and memory management issues.
Neptune takes a holistic approach that considers CPU, memory, network and kernel issues to address these challenges.
This is achieved through optimizations such as application level buffering, batched scheduling, object reuse, built-in support for backpressure and selective compression to ensure better utilization of system resources \cite{buddhika2016neptune}.

Users can deploy stream processing jobs as directed acyclic graphs in Neptune.
A stream processing graph consists of a set of stream ingestion points and stream processors (vertices) and streams connecting these operators (edges).
To provide each job with an initial load-balanced deployment plan, each operator in a stream processing graph can be annotated with a parallelism level while each stream is associated with a partitioning scheme.

\subsection{Synopsis}
\textsc{Synopsis} is a distributed sketch constructed over voluminous data streams.
The number of nodes (or sketchlets) that comprise the sketch varies dynamically as the sketch upscales or downscales to cope with data arrival rates and memory pressure.
Each sketchlet is responsible for one or more geographical scopes and is implemented as a stateful Neptune stream processor that can build and retain state over time.
A stream partitioning scheme, based on the Geohash algorithm (described in Section 3.2), is used to route packets to the appropriate sketchlet.
Sketchlets ingest stream packets and construct compact, in-memory representations of the observational data by extracting metadata from individual stream packets.
During upscaling and downscaling operations, the geographical extents managed by a sketch varies.

Each sketchlet instance extends Neptune's generic stream processor to provide auxiliary services that are needed to construct, update, and maintain the sketch and also to adapt to changing system conditions.
These services include the control plane and the gossip, querying, and monitoring subsystems.

\begin{description}[leftmargin=*]
	\item[Control plane:] The control plane is responsible for orchestrating control messages exchanged between \textsc{Synopsis} nodes as part of various distributed protocols such dynamic scaling.
    It is decoupled from the generic data plane to ensure higher priority and low latency processing without being affected by buffering delays and backpressure during stream processing.

	\item[Gossip subsystem:] While a majority of the \textsc{Synopsis} functionality relies on the local state constructed at a particular node, certain functionalities require an approximate global knowledge.
    For instance, each sketchlet maintains a Geohash prefix tree to assist in distributed query evaluations by forwarding queries to sketchlets that are responsible for particular geographical extents.
        In order to establish and maintain this global view of the entire system, sketchlets gossip about their state periodically (based on time intervals and the number of pending updates) as well as when a change in state occurs.
    \textsc{Synopsis} supports eventual consistency with respect to these updates given their inherent propagation and convergence delays.

	\item[Querying subsystem:] The querying subsystem is responsible for distributed evaluation of queries.
    This involves forwarding queries to relevant sketchlets; in some cases, multiple sketchlets may be involved based on the geographical scope of the query.

    \item[Monitoring subsystem:] Sketchlets comprising \textsc{Synopsis} are probed periodically to gather metrics that impact performance of the system.
    These include memory utilization and backlog information based on rate of packet arrivals and updates to the in-memory structures.
    This information is used for dynamic scaling recommendations as explained in in Section~\ref{subsec:scaling-out}.
\end{description}
